Contention Management for 5G

### 2017-04-25 article/article.tex

      We assume the weight of the central arc to be $0$ since it appears in every route,
      its value does not matter when considering affectations.\\
      Collisions between messages can only appear at node $c_s$ on the way forward and at node $c_t$ on the way back.
      Thus, we only have to check if there is no collisions in a period at those two points.
      We consider two periods P at these vertices, the the {\bf forward period} at $c_s$, and the {\bf backward period} at $c_t$. A message issued by the source $s_1$ at time $m_{s_1}$ will reach $c_s$ at time $m_{s_1} + t(c_s,r_{s_1}) \mod P$ in the forward period, and  $c_t$ at time $m_{t_1} + t(c_t,r_{t_1})\mod P$ in the backward period.
      A $(P,\tau)$-periodic affectation consist in choosing for all $i < n$, $m_i$ and $m_{{\cal C}(s_i)}$ such that, for any couple $(j,k)$,
      we have $[t(c_s,r_{s_{j}})] \cap [t(c_s,r_{s_k})] = \emptyset$ and $[t(c_t,r_{t_j})] \cap [t(c_t,r_{t_k})] = \emptyset$

@@

@@

This algorithm, contrarily to the previous one, may work well, even when the condition $P \geq 3n\tau$ is not true.
In fact, experimental data in Subsection~\cite{} suggest that the algorithm works well as soon as $P \geq ????? \tau$.

	\subsubsection{Exhaustive generation}
% 	\begin{algorithm}[H]
% 	\caption{Exhaustive Generation}  
% 	\begin{algorithmic}
% 	\REQUIRE A routage graph ${\cal R}_{\cal C}$, period $P$, packet size $\tau$
% 	\ENSURE $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$
% 	\STATE Forward-budget $\leftarrow$ $P$ - n * $\tau$
% 	\STATE Backward-budget $\leftarrow$ $P$ - n * $\tau$
% 	\STATE Free-Intervals $\leftarrow$ list of free intervals in the backward period, init to $[0;P[$
% 	\FORALL{source $s_i$ in S}
% 	\FORALL{j in Free-Intervals }
% 	\IF{Message of the route $r_{s_i}$ does not collides with scheduled routes}
% 	\STATE $m_{s_i} \leftarrow $ the first slot of Free-Intervals[j]
% 	\STATE Split the Free-Intervals considering the new packet
% 	\STATE Forward-budget $\leftarrow$ Forward-budget - {\em lost size}
% 	\STATE Backward-budget $\leftarrow$ Backward-budget - {\em lost size}
% 	\STATE call Exhaustive Generation on remaining routes
% 	\ENDIF
% 	\ENDFOR
% 	\ENDFOR
% 
% 
%       \end{algorithmic}
%       \end{algorithm}

@@

>>>>

      We assume the weight of the central arc to be $0$ since it appears in every route,
      its value does not matter when considering affectations.\\
      Collisions between messages can only appear at node $c_s$ on the way forward and at node $c_t$ on the way back.
      Thus, we only have to check if there is no collisions in a period at those two points.
      We consider two periods P at these vertices, the the {\bf forward period} at $c_s$, and the {\bf backward period} at $c_t$. A message issued by the source $s_1$ at time $m_{s_1}$ will reach $c_s$ at time $m_{s_1} + t(c_s,r_{s_1}) \mod P$ in the forward period, and  $c_t$ at time $m_{t_1} + t(c_t,r_{t_1})\mod P$ in the backward period.
      A $(P,\tau)$-periodic affectation consist in choosing for all $i < n$, $m_i$ and $m_{{\cal C}(s_i)}$ such that, for any couple $(j,k)$,
      we have $[t(c_s,r_{s_{j}})] \cap [t(c_s,r_{s_k})] = \emptyset$ and $[t(c_t,r_{t_j})] \cap [t(c_t,r_{t_k})] = \emptyset$.

@@

  \todo{Attention cette simplification n'est pas assez explicite.}

@@

This algorithm, contrarily to the previous one, may work well, even when the condition $P \geq 3n\tau$ is not true.
In fact, experimental data in Subsection~\ref{} suggest that the algorithm works well as soon as $P \geq ????? \tau$.

	\subsubsection{Exhaustive search}
% 	\begin{algorithm}[H]
% 	\caption{Exhaustive Generation}  
% 	\begin{algorithmic}
% 	\REQUIRE A routage graph ${\cal R}_{\cal C}$, period $P$, packet size $\tau$
% 	\ENSURE $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$
% 	\STATE Forward-budget $\leftarrow$ $P$ - n * $\tau$
% 	\STATE Backward-budget $\leftarrow$ $P$ - n * $\tau$
% 	\STATE Free-Intervals $\leftarrow$ list of free intervals in the backward period, init to $[0;P[$
% 	\FORALL{source $s_i$ in S}
% 	\FORALL{j in Free-Intervals }
% 	\IF{Message of the route $r_{s_i}$ does not collides with scheduled routes}
% 	\STATE $m_{s_i} \leftarrow $ the first slot of Free-Intervals[j]
% 	\STATE Split the Free-Intervals considering the new packet
% 	\STATE Forward-budget $\leftarrow$ Forward-budget - {\em lost size}
% 	\STATE Backward-budget $\leftarrow$ Backward-budget - {\em lost size}
% 	\STATE call Exhaustive Generation on remaining routes
% 	\ENDIF
% 	\ENDFOR
% 	\ENDFOR
% 
% 
%       \end{algorithmic}
%       \end{algorithm}

@@

     \todo{Il faut faire une présentation modulaire avec d'un coté choix de de départ des messages, ->LS, ->SL, ->RANDOM
     puis choix de retour, Greedy et Optimal. Ensuite on montre que dans le cas simple de toutes les arêtes de départ à la même valeur,
     LSG est optimal (dire que c'est un cas raisonnable). Éventuellement deux valeurs différentes serait raisonnable mais je n'ai pas trouvé de bons algos.
     Ensuite il faut expliquer proprement greedy et Simons (sans donner tous les détails pour Simons) et expliquer les limitations -> pas de gestion de la période pour Simons.
     On peut gérer la période pour Simons en bruteforce sur les routes. Il faut que j'écrive mes algos FPTs en le nombre de routes même si on ne les implémente pas.}
